---
title: "Diagnostics for assessing the accuracy of linear noise and moment closure approximations"
author: "Colin Gillespie & Andrew Golightly"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
---

```{r echo=FALSE}
source("lv_plots.R")
```


This dashboard contains additional graphics for the paper

> Gillespie, C.S. Diagnostics for assessing the accuracy of linear noise and moment
    closure approximations, 2016.

The graphics below relate to Examples 4.2 and 4.3 in the paper. Since the dataset
in Example 4.3 was large, we have sampled 2500 points to make download times smaller.


Predator & Prey (Ex 4-2)
===================================== 

Column 
-------------------------------------

### Probability of prey death (t=10)

```{r}
maxtime=10
g1 = make_plot(maxtime)+geom_point(aes(colour=Extreme, size=prey_death, 
                                  text=paste("Prob of prey death: ", prey_death)))
ggplotly(g1, tooltip = c("x", "y", "text"))%>% layout(showlegend = FALSE)
```

### Probability of prey death (t=30)

```{r}
maxtime=30
g1 = make_plot(maxtime)+geom_point(aes(colour=Extreme, size=prey_death,
                                  text=paste("Prob of prey death: ", prey_death)))
ggplotly(g1, tooltip = c("x", "y", "text"))%>% layout(showlegend = FALSE)
```

### Probability of prey death  (t=100)

```{r}
maxtime=100
g1 = make_plot(maxtime)+geom_point(aes(colour=Extreme, size=prey_death,
                                  text=paste("Prob of prey death: ", prey_death)))
ggplotly(g1, tooltip = c("x", "y", "text"))%>% layout(showlegend = FALSE)
```

Column
-------------------------------------

### Probability of predator death (t=10)

```{r}
maxtime=100
g2 = make_plot(maxtime)+geom_point(aes(colour=Extreme, size=pred_death,
                                  text=paste("Prob of pred death: ", pred_death)))
ggplotly(g2, tooltip = c("x", "y", "text"))%>% layout(showlegend = FALSE)

```

### Probability of predator death (t=30)

```{r}
maxtime=100
g2 = make_plot(maxtime)+geom_point(aes(colour=Extreme, size=pred_death,
                                  text=paste("Prob of pred death: ", pred_death)))
ggplotly(g2, tooltip = c("x", "y", "text"))%>% layout(showlegend = FALSE)

```

### Probability of predator death (t=100)

```{r}
maxtime=100
g2 = make_plot(maxtime)+geom_point(aes(colour=Extreme, size=pred_death,
                                  text=paste("Prob of pred death: ", pred_death)))
ggplotly(g2, tooltip = c("x", "y", "text"))%>% layout(showlegend = FALSE)

```


Prokaryotic auto regulatory gene network (Ex 4-3)
====================================================

Column
-------------------------------------

### Species I

```{r}
source("auto_reg.R")
I = 6
f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "#7f7f7f"
)
x <- list(
  title = "Std. Residual",
  titlefont = f
)
y <- list(
  titlefont = f
)

plot_ly(x = dd_prior[,I], type = "histogram", name="Prior") %>%
  add_trace(x = dd_post[,I], opacity = 0.6, type = "histogram", name="Posterior") %>%
  layout(barmode="overlay")%>%
  layout(title = "Histogram of Std Residuals", xaxis = x, yaxis = y)
```

### Species i

```{r}
I = 4
plot_ly(x = dd_prior[,I], type = "histogram", name="Prior") %>%
  add_trace(x = dd_post[,I], opacity = 0.6, type = "histogram", name="Posterior") %>%
  layout(barmode="overlay")%>%
  layout(xaxis = x, yaxis = y)
```

Column
-------------------------------------

### Species I
```{r}
I = 6
dd1 = qqnorm(dd_prior[,I], plot.it=F); 
dd2 = qqnorm(dd_post[,I],  plot.it=F); 

f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "#7f7f7f"
)
x <- list(
  title = "Theortical quantiles",
  titlefont = f
)
y <- list(
  title = "Sample quantiles",
  titlefont = f
)
plot_ly(x=dd1$x, y = dd1$y, mode = "markers", name="Prior") %>%
  add_trace(x=dd2$x, y = dd2$y,opacity = 0.6, mode="markers", name="Posterior") %>%
    layout(title = "q-qplot of Std Residuals", xaxis = x, yaxis = y)
```


### Species i

```{r}
I = 4
dd1 = qqnorm(dd_prior[,I], plot.it=F); 
dd2 = qqnorm(dd_post[,I],  plot.it=F); 

plot_ly(x=dd1$x, y = dd1$y, mode = "markers", name="Prior") %>%
  add_trace(x=dd2$x, y = dd2$y,opacity = 0.6, mode="markers", name="Posterior") %>%
    layout( xaxis = x, yaxis = y)
```

column 
-------------------------------------

### Species I 

```{r}
x <- list(
  title = "log(c2)",
  titlefont = f
)
y <- list(
  title = "Std residual",
  titlefont = f
)


I = 6
plot_ly(x = log(pars_prior[dd_prior[,7]+1,3]), y = dd_prior[,I], mode="markers", name="Prior") %>%
    add_trace(x=log(pars_prior[dd_prior[,7]+1,3]), y = dd_post[,I],opacity = 0.6, mode="markers", name="Posterior")  %>%
    layout(title = "Std. Res vs parameter", xaxis = x, yaxis = y)


```
 
### Species i 

```{r}
I = 4
plot_ly(x = log(pars_prior[dd_prior[,7]+1,3]), y = dd_prior[,I], mode="markers", name="Prior") %>%
    add_trace(x=log(pars_prior[dd_prior[,7]+1,3]), y = dd_post[,I],opacity = 0.6, mode="markers", name="Posterior") %>%
    layout(xaxis = x, yaxis = y)
```














